\makeatletter\let\ifGm@compatii\relax\makeatother
\documentclass[red]{beamer}

%\usepackage{beamerthemesplit}
\usepackage{listings}
\usepackage{comment}
\usepackage{url}
\usepackage{bm}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{shapes.symbols}

\usepackage{hyperref} % has to be last
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdfpagemode=FullScreen,
    }

\tikzset{
    saiarrow/.style={{-Latex}, thick}
}

\newcommand{\isred}[1]{{\color{red} {\bf #1}}} 
\newcommand{\isblue}[1]{{\color{blue}{\bf #1}}} 
\newcommand{\isgreen}[1]{{\color{green} {#1}}} 
\newcommand{\isdarkgreen}[1]{{\color{darkgreen} {#1}}} 
\newcommand{\isorange}[1]{{\color{orange} {#1}}} 

\DeclareMathOperator{\poly}{poly}

\begin{document}


\setbeamercolor{alerted_text}{fg=cyan}
\xdefinecolor{purplish}{cmyk}{0.75,0.75, 0, 0}
\xdefinecolor{purple}{cmyk}{0.75,0.75, 0, 0}
\colorlet{newred}{red!60!black}

\title{Session 7: Final Exam}
\author{Slides prepared by UMBC Protocol Analysis Lab}
\date{Last edited \today}
\begin{frame}
\maketitle
\end{frame}

\begin{frame}\frametitle{Final Exam Instructions}
\begin{itemize}
\item The final exam will occur between 6:05 PM and 7:00 PM
\item You will have 55 minutes plus 10 minutes of grace time to upload your solutions.
The form will close at 7:10.
\item You may use your notes, the slides, the lecture recordings, the GitHub, the CPSA manual. 
You can also ask us for help.
\item You may not use any other resources, including asking other people in the class.
\item Once you have submitted, you are free to leave (the lab or the Discord).
\item Try your best! The exam is mostly for us to see how well we've taught, rather than to ``grade'' you.
\end{itemize}
\end{frame}

\begin{frame}\frametitle{Survey}
Fill in details about the survey here!
\end{frame}
\end{document}