\makeatletter\let\ifGm@compatii\relax\makeatother
\documentclass[red]{beamer}

%\usepackage{beamerthemesplit}
\usepackage{listings}
\usepackage{comment}
\usepackage{url}
\usepackage{bm}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{shapes.symbols}

\usepackage{hyperref} % has to be last
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdfpagemode=FullScreen,
    }

\tikzset{
    saiarrow/.style={{-Latex}, thick}
}

\newcommand{\isred}[1]{{\color{red} {\bf #1}}} 
\newcommand{\isblue}[1]{{\color{blue}{\bf #1}}} 
\newcommand{\isgreen}[1]{{\color{green} {#1}}} 
\newcommand{\isdarkgreen}[1]{{\color{darkgreen} {#1}}} 
\newcommand{\isorange}[1]{{\color{orange} {#1}}} 

\DeclareMathOperator{\poly}{poly}

\begin{document}


\setbeamercolor{alerted_text}{fg=cyan}
\xdefinecolor{purplish}{cmyk}{0.75,0.75, 0, 0}
\xdefinecolor{purple}{cmyk}{0.75,0.75, 0, 0}
\colorlet{newred}{red!60!black}

\title{Session 8: Final Presentations}
\author{Slides prepared by UMBC Protocol Analysis Lab}
\date{Last edited \today}
\begin{frame}
\maketitle
\end{frame}

\begin{frame}
\begin{center}
{\huge Presentation order}
\end{center}
\begin{itemize}
\item names names
\item names names
\end{itemize}

\end{frame}

\begin{frame} \frametitle{Join UMBC PAL!}
    \begin{itemize}
        \item If you liked the things you learned about during the workshop, join us in the lab!
        \item UMBC PAL does protocol analysis, digital provenance, and AI security
        \item We need math (proofs), computer science (coding), and all kinds of other skills
        \item Meetings on Fridays at 1PM on Discord or in ITE 228
        \item If you have any questions about joining a project, let one of us know.
    \end{itemize}
\end{frame}


\begin{frame}\frametitle{Conclusion}
\begin{itemize}
\item Thank you all for joining us for these eight sessions!
\item Hopefully you learned something, and are interested in joining PAL.
\item We are aiming to produce a paper about teaching cybersecurity.
When the paper is published, everyone will be acknowledged for their participation (by session number).
\item Session 1: We did not have IRB approval, so no data collected for study.
Your certificate is still valid, and you will still be acknowledged, we just won't use any data from this round.
\end{itemize}
\end{frame}

\begin{frame}\frametitle{Survey}
Fill in details about the survey here!
\end{frame}
\end{document}